---
title: "Slay the Word"
author: "Mark Andrews"
date: "13 July 2018"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE)
```

```{r load_packages}
library(tibble)
library(dplyr)
library(ggplot2)
library(pander)
```

A univariate normal, or Gaussian, linear model is defined as follows. Assume that our data consists of $n$ independent pairs of observations:
$$
\mathcal{D} = \{(y_1, \vec{x}_1) \ldots (y_i, \vec{x}_i) \ldots (y_n, \vec{x}_n)\},
$$
where each $y_i \in \mathbb{R}$ and $\vec{x}_i \in \mathbb{R}^K$. We then model this data as follows:
$$
y_i \sim N(\beta_0 + \sum_{k=1}^{K} \beta_k x_{ik}, \sigma^2),\quad \text{for $i \in \{1,2 \ldots n\}$}.
$$

# Demonstration

Here, we generate some data.
```{r fake_data}
N <- 50
Df <- tibble(x = rnorm(N),
             y = 1.25 + 2.25*x + rnorm(N),
             z = sample(c('yes','no'), size=N, replace=T)
)
```

```{r scatterplot, fig.cap='Scatterplot with line of best fit.', fig.width=5}
Df %>% ggplot(mapping=aes(x=x, y=y, col=z)) +
  geom_point() +
  stat_smooth(method = 'lm') +
  theme_classic()
```

Here, we fit the model with maximum likelihood estimation:
```{r linear_model}
M <- lm(y ~ x + z, data=Df)
pander(summary(M))
```

## Inserting images

![This image is inserted.](pdf_image.pdf)